---
title: "Custom Syntax Highlighting for {distill} Part 2: Creating the Palette"
description: |
  Post description
author: 
  - name: Ella Kaye
    url: https://twitter.com/ellamkaye
date: '2021-05-22'
base_url: https://ellakaye.rbind.io/
preview: IMAGE.png
categories:
  - TAG_1
  - TAG_2
twitter:
  site: "@ellamkaye"
  creator: "@ellamkaye"
output:
  distill::distill_article:
    highlight: /Users/ellakaye/ellakaye-distill/ek_syntax_highlighting.theme
    self_contained: false
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = TRUE,
  message = TRUE,
  R.options = list(width = 60)
)
```

```{r metathis, message=FALSE, warning=FALSE, include=FALSE}
library(metathis)

meta() %>%
  meta_name("github-repo" = "ellakaye/ellakaye-distill") %>%
  meta_viewport() %>%
  meta_social(
    title = "TITLE", # adding title here removes "ELLA KAYE: " from the front
    image = "https://ellakaye.rbind.io/posts/FULL_PATH_TO_IMAGE.png", 
    image_alt = "ALT TEXT FOR IMAGE",
    og_type = "website",
    og_author = c("Ella Kaye"),
    twitter_card_type = "summary_large_image", # can also be summary
  )
```

In Part 1 of this series, [custom syntax highlighting for {distill}: modifying the theme **LINK**](), I described why and how I went about the process of finding and modifying the default syntax highlighting for [{distill}]((https://rstudio.github.io/distill/)) and how I created a function for [{distilltools}](https://ellakaye.github.io/distilltools). I also outlined the four criteria that were important to me as I went about choosing colours for my own syntax highlighting theme:

- It be based around <span style="color:#D4006A">the pink</span> that I use in my logo and elsewhere throughout this site
- It uses colour theory to pick colours that all look appealing together
- It meets [WCAG web accessibility guidelines](https://www.w3.org/WAI/standards-guidelines/wcag/), by ensuring sufficient colour contrast between the colours in the theme and this site's background colour (white)
- The colours in the palette are colourblind-friendly, i.e. still distinguishable to people with various difference types of colourblindness.

This post spins out from Part 1 with a deep-dive into the processes, both thought and practical, of choosing colours for my palette that met the above criteria.

This post brings two-for-one value - not only do I write up how I first went about this to derive the palette that's implemented throughout this site, I also demonstrate a totally different, entirely R-based, alternative approach to satisfying the criteria!
