---
title: Ranking Items Scalably with the Bradley-Terry Model
description: |
  Introducing the `BradleyTerryScalable` package
author: 
  - name: Ella Kaye
    url: {}
date: '2017-07-06'
output:
  distill::distill_article:
    self_contained: false
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries}
library(distilltools)
```

```{r icon-links}
# [TODO]: fill in urls
# [TODO]: delete any unessary icons (or add more)
# [TODO]: css styling for .icon-link and .icon-link:hover
# [NOTE]: icons in same chunk will appear on same line
# [NOTE]: icons in different chunks will appear on a different lines
icon_link(
  icon = "images",
  text = "slides",
  url = "https://ellakaye.github.io/useR-2017-talk/useR_presentation.html#1"
)

icon_link(
  icon = "github",
  text = "materials",
  url = "https://github.com/EllaKaye/useR-2017-talk"
)

icon_link(
  icon = "box-open",
  text = "package",
  url = "https://ellakaye.github.io/BradleyTerryScalable/"
)
```

## Overview 

I am very excited to be introducing the package `BradleyTerryScalable` at useR!2017. The package is available on [GitHub](https://github.com/EllaKaye/BradleyTerryScalable).

`BradleyTerryScalable` is an R package for fitting the Bradley-Terry model to pair-comparison data, to enable statistically principled ranking of a potentially large number of objects.

Given a number of items for which we have pair-comparison data, the Bradley-Terry model assigns a ‘strength’ parameter to each item. These can be used to rank the items. Moreover, they can be used to determine the probability that any given item will ‘beat’ any other given item when they are compared. Further details of the mathematical model, and the algorithms used to fit it, are available in the package [vignette](https://ellakaye.github.io/BradleyTerryScalable/articles/BradleyTerryScalable.html).

## Event details

**Event:** [useR!2017](https://user2017.brussels)

**Date:** July 6th, 2017

**Time:** 11:36 AM

**Location:** Brussels, Belgium

## Slides

Keyboard Shortcuts for Slides:

- Use <kbd>←</kbd> and <kbd>→</kbd> to navigate through the slides.
- Use <kbd>f</kbd> to toggle full screen.
- Use <kbd>o</kbd> to view an overview of all slides.
- Use <kbd>h</kbd> to see a list of other shortcuts.

```{r slides, echo=FALSE}
xaringanExtra::embed_xaringan(
  url = "https://ellakaye.github.io/useR-2017-talk/useR_presentation.html#1",
  ratio = "4:3"
)
```
