---
title: Testing short icon names
description: |
  Talk description
author: 
  - name: Ella Kaye
    url: {}
date: '2021-05-02'
output:
  distill::distill_article:
    self_contained: false
    toc: true
draft: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries}
library(distilltools)
library(fontawesome)
```

## Short names
```{r icon-links}
# [TODO]: fill in urls
# [TODO]: delete any unessary icons (or add more)
# [TODO]: css styling for .icon-link and .icon-link:hover
# [NOTE]: icons in same chunk will appear on same line
# [NOTE]: icons in different chunks will appear on a different lines
icon_link(
  icon = "images", #fas fa-images
  text = "slides",
  url = "https://ellakaye.github.io/Rladies-Coventry-getting-help-in-R/getting_help_in_R.html#1"
)

icon_link(
  icon = "images", #fas fa-images
  text = "slides",
  url = "https://ellakaye.github.io/Rladies-Coventry-getting-help-in-R/getting_help_in_R.html#1",
  style = "regular"
)

icon_link(
  icon = "github",
  text = "materials",
  url = "https://github.com/EllaKaye/Rladies-Coventry-getting-help-in-R"
)

icon_link(
  icon = "play-circle",
  text = "video",
  url = "https://www.youtube.com/watch?v=YhR1gKhWmxs&t=1661s"
)
```

Long names:

```{r icon-links-long}
# [TODO]: fill in urls
# [TODO]: delete any unessary icons (or add more)
# [TODO]: css styling for .icon-link and .icon-link:hover
# [NOTE]: icons in same chunk will appear on same line
# [NOTE]: icons in different chunks will appear on a different lines
# should be regular
icon_link(
  icon = "far fa-images", #fas fa-images
  text = "slides",
  url = "https://ellakaye.github.io/Rladies-Coventry-getting-help-in-R/getting_help_in_R.html#1"
)

# should be solid
icon_link(
  icon = "fas fa-images", #fas fa-images
  text = "slides",
  url = "https://ellakaye.github.io/Rladies-Coventry-getting-help-in-R/getting_help_in_R.html#1",
  style = "regular"
)

icon_link(
  icon = "fab fa-github",
  text = "materials",
  url = "https://github.com/EllaKaye/Rladies-Coventry-getting-help-in-R"
)

icon_link(
  icon = "fas fa-play-circle",
  text = "video",
  url = "https://www.youtube.com/watch?v=YhR1gKhWmxs&t=1661s"
)
```


```{r}
make_icon("google-scholar")
make_icon("orcid")
make_icon("fab fa-orcid")
make_icon("ai ai-orcid")
make_icon("ai ai-mendeley")
make_icon("fab fa-mendeley")
make_icon("mendeley")
make_icon("behance")
make_icon("fab fa-behance")
make_icon("researchgate")
make_icon("fab fa-behance")
```

## researchgate:
```{r}
icon_link("researchgate", "short")
icon_link("ai ai-researchgate", "ACAD, full")
icon_link("fab fa-researchgate", "FA, full")
```

## orcid:
```{r}
icon_link("orcid", "short")
icon_link("ai ai-orcid", "ACAD, full")
icon_link("fab fa-orcid", "FA, full")
```

## mendeley:
```{r}
icon_link("mendeley", "short")
icon_link("ai ai-mendeley", "ACAD, full")
icon_link("fab fa-mendeley", "FA, full")
```

```{r}
icon_link("google-scholar", "Google Scholar", "https://scholar.google.com")
icon_link("orcid", "orcid (short - ai)", url = "https://google.com")
icon_link("fab fa-orcid", "orcid fa full", url = "https://google.com")
icon_link("ai ai-orcid", "orcid (acad)", url = "https://google.com")
```

```{r}
icon_link("arxiv", "arxiv", "https://arxiv.org")
```

## other academicons
```{r}
icon_link("ceur", "ceur", "https://scholar.google.com")
icon_link("datacite", "datacite", "https://datacite.org")
```

# get warning but still knit and link?
```{r}
icon_link("images", "images", url = "https://twitter.com/home", style = "brands")
```



```{r}
library(dplyr)
library(stringr)
i_n <- distilltools:::icon_names %>%
  as_tibble()

i_n %>%
  filter(full_name == "ai ai-orcid")

i_n %>%
  filter(str_detect(name, "google"))

i_n %>%
  filter(name == "researchgate")
```

# fontawesome package

```{r}
fa_i("orcid")
fa_orcid <- fa_i("orcid")
as.character(fa_orcid)

fa_i("researchgate")
fa_rg <- fa_i("researchgate")
as.character(fa_rg)
```

- with all: <i class="fab fa-orcid" role = "presentation" aria-label="orcid icon"></i>
- without role: <i class="fab fa-orcid" aria-label="orcid icon"></i>
- without aria label: <i class="fab fa-orcid" role = "presentation"></i>
- with just class: <i class="fab fa-orcid"></i>

- now back to make_icon (short): `r make_icon("orcid")`
- now back to make_icon (full fa): `r make_icon("fab fa-orcid")`
- now back to make_icon (full ai): `r make_icon("ai ai-orcid")`

- now back to icon_link (short): `r icon_link("orcid")`
- now back to icon_link (full fa): `r icon_link("fab fa-orcid")`
- now back to icon_link (full ai): `r icon_link("ai ai-orcid")`

## Overview 


## Event details

**Event:** [GROUP](url)

**Date:** DATE

**Location:** LOCATION

## Key points

- Point 1
- Point 2
- ...

## Slides

Keyboard Shortcuts for Slides:

- Use <kbd>←</kbd> and <kbd>→</kbd> to navigate through the slides.
- Use <kbd>f</kbd> to toggle full screen.
- Use <kbd>o</kbd> to view an overview of all slides.
- Use <kbd>h</kbd> to see a list of other shortcuts.

```{r slides, echo=FALSE}
xaringanExtra::embed_xaringan(
  url = "url")
```

# Raw html


