---
title: Setting up you PhD (or other research project!) as an R package
description: |
  How I set up my PhD as an R package
author: 
  - name: Ella Kaye
    url: {}
date: '2018-08-23'
base_url: https://ellakaye.rbind.io/
preview: phd-as-package.png
output:
  distill::distill_article:
    self_contained: false
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries}
library(distilltools)
```

```{r icon-links}
# [TODO]: fill in urls
# [TODO]: delete any unessary icons (or add more)
# [TODO]: css styling for .icon-link and .icon-link:hover
# [NOTE]: icons in same chunk will appear on same line
# [NOTE]: icons in different chunks will appear on a different lines
icon_link(#icon = "fas fa-images",
          icon = "images",
          text = "slides",
          url = "https://ellakaye.github.io/BirminghamR-talk/PhD_to_package_birmR.html#1")

icon_link(#icon = "fab fa-github",
          icon = "github",
          text = "materials",
          url = "https://github.com/EllaKaye/BirminghamR-talk")
```

## Overview 
In this talk, I will try to convince you that if you have any of your own data or write any of your own R functions, then you should put them into an R package. Benefits include reproducibility and keeping everything together and accessible. Also, it’s really easy to do, and to prove it, I will build a package from scratch before your very eyes. I will also introduce the `bookdown` package for writing reports and even your thesis. Filled with tips and tricks from my own experiences, this talk could save you hours!

## Event details

**Event:** [Birmingham R User Group](https://www.meetup.com/BirminghamR/events/253456048/?gj=co2&rv=co2&_xtd=gatlbWFpbF9jbGlja9oAJGE0MGZmNDA5LTFlMjctNDFhNS04ODgzLTM4MGU2ZWViM2Y3OQ)

**Date:** August 8th, 2018

**Time:** 18:00-20:00 GMT+1

**Location:** Faraday Wharf, Innovation Birmingham Campus, Holt Street, Birmingham Science Park, B7 4BB


## Slides

Keyboard Shortcuts for Slides:

- Use <kbd>←</kbd> and <kbd>→</kbd> to navigate through the slides.
- Use <kbd>f</kbd> to toggle full screen.
- Use <kbd>o</kbd> to view an overview of all slides.
- Use <kbd>h</kbd> to see a list of other shortcuts.

```{r slides, echo=FALSE}
xaringanExtra::embed_xaringan(
  url = "https://ellakaye.github.io/BirminghamR-talk/PhD_to_package_birmR.html#1",
  ratio = "4:3"
)
```
