---
title: "Working with text in R"
description: |
  An overview of a range of packages for working with text in R..
author: Ella Kaye
date: 2020-07-04
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries}
library(distilltools)
```

```{r icon-links}
# [TODO]: fill in urls
# [TODO]: delete any unessary icons (or add more)
# [TODO]: css styling for .icon-link and .icon-link:hover
# [NOTE]: icons in same chunk will appear on same line
# [NOTE]: icons in different chunks will appear on a different lines
icon_link(icon = "fas fa-images",
          text = "slides (full screen)",
          url = "")

icon_link(icon = "fas fa-file-pdf",
          text = "slides (PDF)",
          url = "")

icon_link(icon = "fab fa-github",
          text = "materials",
          url = "")

icon_link(icon = "fas fa-play-circle",
          text = "video",
          url = "")

icon_link(icon = "fas fa-folder-open",
          text = "project",
          url = "")
```

Transcending its origins as a programming language for statistics, R provides excellent tools for working with text. This tidyverse-based talk will provide an overview of some of the fantastic packages available for this, including (but not limited to) `stringr`, `RVerbalExpressions`, `tidytext` and `wordcloud`.

## Take home messages

-
-

# Event details

**Event:** RLadies Tbilisi

**Date:** July 4th, 2020

** Location:** Zoom

# Event details

**Event:** RLadies Toronto

**Date:** July 4th, 2020

** Location:** Zoom

  
