---
title: An Overview of htmlwidgets
description: |
  A brief overview of htmlwidgets in R
author: 
  - name: Ella Kaye
    url: {}
date: '2017-05-25'
output:
  distill::distill_article:
    self_contained: false
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries}
library(distilltools)
```

```{r icon-links}
# [TODO]: fill in urls
# [TODO]: delete any unessary icons (or add more)
# [TODO]: css styling for .icon-link and .icon-link:hover
# [NOTE]: icons in same chunk will appear on same line
# [NOTE]: icons in different chunks will appear on a different lines
icon_link(
  icon = "images",
  text = "slides",
  url = "https://ellakaye.shinyapps.io/htmlwidgets_overview/#1"
)

icon_link(
  icon = "github",
  text = "materials",
  url = "https://github.com/EllaKaye/htmlwidgets_WRUG_pres"
)
```

## Overview 

The [`htmlwidgets`](http://www.htmlwidgets.org/index.html) package allows developers to create R bindings to JavaScript libraries. The resulting R packages allow the embedding of interactive content in R Markdown documents and Shiny web apps. There are over 50 available widgets. In this talk I give an overview of the `htmlwidget` framework and demonstrate the use of the [`DT`](https://rstudio.github.io/DT/), [`leaflet`](http://rstudio.github.io/leaflet/) and [`DiagrammeR`](http://rich-iannone.github.io/DiagrammeR/) packages.

## Event details

**Event:** [Warwick R User Group](https://warwick.ac.uk/fac/sci/wdsi/events/wrug/)

**Date:** May 25th, 2017

**Time:** 17:00 

**Location:** University of Warwick

