---
title: "Working with text in R"
description: |
  An overview of a range of packages for working with text in R.
author: Ella Kaye
base_url: https://ellakaye.rbind.io/
preview: working-with-text-in-r.png
date: 2019-10-05
output:
  distill::distill_article:
    self_contained: false
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries}
library(distilltools)
```

```{r icon-links}
# [TODO]: fill in urls
# [TODO]: delete any unessary icons (or add more)
# [TODO]: css styling for .icon-link and .icon-link:hover
# [NOTE]: icons in same chunk will appear on same line
# [NOTE]: icons in different chunks will appear on a different lines
icon_link(icon = "images",
          text = "slides",
          url = "https://ellakaye.github.io/RLadies-Tbilisi-talk/text_in_R_Tbilisi.html#1")

icon_link(icon = "github",
          text = "materials",
          url = "https://github.com/EllaKaye/RLadies-Tbilisi-talk")

icon_link(icon = "play-circle",
          text = "video",
          url = "https://youtu.be/AnVzb5XI0Iw")
```

## Overview

Transcending its origins as a programming language for statistics, R provides excellent tools for working with text. This tidyverse-based talk will provide an overview of some of the fantastic packages available for this, including (but not limited to) `stringr`, `RVerbalExpressions`, `tidytext`, `wordcloud` and `ggwordcloud`.

## Event details

**Event:** RLadies Toronto

**Date:** October 5th, 2019

**Time:** 14:00-16:00 EDT

**Location:** Stewart Building, 149 College Street, Toronto

I then gave an updated version of the talk a few months later (links at the top relate to this version):

**Event:** RLadies Tbilisi

**Date:** July 4th, 2020

**Time:** 09:00-10:00 GMT

**Location:** Zoom

## Slides

Keyboard Shortcuts for Slides:

- Use <kbd>←</kbd> and <kbd>→</kbd> to navigate through the slides.
- Use <kbd>f</kbd> to toggle full screen.
- Use <kbd>o</kbd> to view an overview of all slides.
- Use <kbd>h</kbd> to see a list of other shortcuts.

```{r slides, echo=FALSE}
xaringanExtra::embed_xaringan(
  url = "https://ellakaye.github.io/RLadies-Tbilisi-talk/text_in_R_Tbilisi.html#1",
  ratio = "4:3")
```

