---
title: "How to get help in R"
description: |
  Tips for looking for answers and asking questions about R
author: Ella Kaye
date: 2020-10-29
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries}
library(distilltools)
```

```{r icon-links}
# [TODO]: fill in urls
# [TODO]: delete any unessary icons (or add more)
# [TODO]: css styling for .icon-link and .icon-link:hover
# [NOTE]: icons in same chunk will appear on same line
# [NOTE]: icons in different chunks will appear on a different lines
icon_link(icon = "fas fa-images",
          text = "slides (full screen)",
          url = "https://ellakaye.github.io/Rladies-Coventry-getting-help-in-R/getting_help_in_R.html#1")

icon_link(icon = "fab fa-github",
          text = "materials",
          url = "https://github.com/EllaKaye/Rladies-Coventry-getting-help-in-R")

icon_link(icon = "fas fa-play-circle",
          text = "video",
          url = "https://www.youtube.com/watch?v=YhR1gKhWmxs&t=1661s")
```
  
# Abstract

This session will be led by Ella Kaye - an R enthusiast and statistics PhD researcher at the University of Warwick. In the session, Ella will talk us through different ways to get help when you get stuck on a problem in R. We’ll cover how and where to look for answers and how to ask and post good questions that make it easy for others to help you, including a demo of the excellent `reprex` and `datapasta` packages. So whether you’re an R novice or more experienced R user, hopefully there’ll be some useful tips for you!

# Take home messages

- When faced with a question/problem, have a good look - for an answer in R itself and/or online
- Don't be shy to ask questions!
- Write reproducible examples
- Give thought to where you ask/post your question
- Give back by helping others

# Event details: [R Ladies Coventry](https://www.meetup.com/rladies-coventry/events/273429872/)

Date: October 29th, 2020 (the inaugural talk)
Location: Zoom

# Event details: [bseeR](https://www.ellenwebborn.com/rusergroup/)

Date: January 28th, 2021
Location: Microsoft Teams



